Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2019-03-15 Paper/RSVOptimization.rnw
Discussion tweaks

\subsection{Conclusions}

@@

Our effort to optimize timing of the prophylaxis regimen (without changing its duration, and therefore its pharmaceutical cost) shows the possibility of a theoretical 1-2\% statewide decrease in RSV-associated hospitalizations among high-risk infants each year, primarily in counties with higher RSV burden (Fairfield, Hartford, and New Haven counties). The magnitude of that improvement wanes upon encountering practicalities of clinical practice guideline implementation. Nonetheless, with clinical practice guidelines localized at the county level, and the timing of prophylaxis adjusted in each county by less than a whole month from the current AAP guidelines, we still found the potential for $\sim$1\% statewide decrease in RSV-associated hospitalizations among high risk infants. The prophylaxis regimen with which we were able to attain this improvement is the one in which prophylaxis in each county is timed relative to the midpoint of the RSV season (rounded to two weeks) in that county, which simultaneously reduces unprotected cases early in the season and ineffective prophylaxis late in the season. Increasing complexity of practice guidelines carries with it increased cost of implementation, such as training of clinicians and other healthcare workers. It is therefore not apparent from our research alone that the potential benefits would outweigh the costs.

>>>>

\subsection{Results}

@@

Our effort to optimize timing of the prophylaxis regimen (without changing its duration, and therefore its pharmaceutical cost) shows a theoretical 1-2\% statewide decrease in RSV-associated hospitalizations among high-risk infants each year, primarily in counties with higher RSV burden (Fairfield, Hartford, and New Haven counties). The magnitude of that improvement declines after accounting for practicalities of clinical practice guideline implementation. Nonetheless, with clinical practice guidelines localized at the county level, and the timing of prophylaxis adjusted in each county by less than a whole month from the current AAP guidelines, we still found the potential for $\sim$1\% statewide decrease in RSV-associated hospitalizations among high risk infants. The prophylaxis regimen with which we were able to attain this improvement is the one in which prophylaxis in each county is timed relative to the midpoint of the RSV season (rounded to two weeks) in that county, which simultaneously reduces unprotected cases early in the season and ineffective prophylaxis late in the season. Increasing complexity of practice guidelines would carry with it increased cost of implementation (such as training of clinicians and other healthcare workers); it is therefore not apparent from our research alone that the potential benefits would outweigh the costs.
